miniKanren with fair search

### 2019-03-17 Paper/paper.tex
tuning Introduction

The best way to write a miniKanren program can depend on the search strategy. For example, with inteleaving depth-first search (iDFS), users sometimes need to order their conde clauses carefully to avoid starving later clauses. This is because iDFS spends half of computation effort on the first clause, a quater on the second, and so on. Seasoned miniKanreners usually know how to make use of this bias to optimize their programs. However, we believe search strategies less sensitive to conde clause order can also be useful. We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and answer order of some known miniKanren programs. The experiment is conducted within the miniKanren in \textit{The Reasoned Schemer, 2nd Edition}.

%TODO use microKanren instead?

%The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
%an efficient and complete search strategy -- interleaving depth-first search (iDFS).
%iDFS biases toward left conde lines. So miniKanren programmers sometimes need to
%organize their conde lines carefully. We propose and implement two search strategies,
%breadth-first search (BFS) and balanced interleaving DFS (biDFS). With either of these
%search strategy, miniKanren becomes less sensitive to the order of conde lines.

Section 2 explains why iDFS biases toward left conde clauses. Section 2 is about the biDFS. Section 3 is about BFS.

@@

The results are not cost-respecting. For example, \texttt{'(a a)} occurs before
\texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
iDFS strategy is the cause, since it prioritizes the first \texttt{conde} case
considerablely. When every conde case are equally productive, the iDFS
strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
which share the same portion as the second last one.

>>>>

With interleaving depth-first search, disjunctive operator allocates half computational effort to its first goal, and quater to the second, eighth to the third, and so on. Consequently, miniKanren programmers sometimes need to order their \texttt{conde} clauses carefully to prevent some clauses absorbing unproportional computational effort. For example, when a relational proof checker is used as a proof generator, the eliminational rules should comes later.
%TODO KC: prefer an example from other literatures 
Seasoned miniKanreners usually know how to make use of this unfair allocation to optimize their programs. However, we believe search strategies less sensitive to goal order can also be useful to little miniKanreners as well as seansoned ones. We propose two such search strategies, balanced interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they affect the efficiency and query result of known miniKanren programs. The experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 2nd Edition}.

%TODO KC: Should we use microKanren instead?

%The version of miniKanren in \textit{The Reasoned Schemer, 2nd Edition} features
%an efficient and complete search strategy -- interleaving depth-first search (iDFS).
%iDFS biases toward left \texttt{conde} lines. So miniKanren programmers sometimes need to
%organize their \texttt{conde} lines carefully. We propose and implement two search strategies,
%breadth-first search (BFS) and balanced interleaving DFS (biDFS). With either of these
%search strategy, miniKanren becomes less sensitive to the order of \texttt{conde} lines.

(TODO: summarize following sections) Section 2 explains why iDFS biases toward left \texttt{conde} clauses. Section 3 is about the biDFS. Section 3 is about BFS.

@@

The results are not cost-respecting. For example, \texttt{'(a a)} occurs before
\texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
iDFS strategy is the cause, since it prioritizes the first \texttt{conde} case
considerablely. When every \texttt{conde} case are equally productive, the iDFS
strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
which share the same portion as the second last one.
